Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-07 project.after.Rmd
minor edit

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("final.model")) {
  cat(" fitting...")
  final.model <- Arima(final.training, chosen.model[1:3], chosen.model[4:6], lambda=chosen.lambda)
  cat("DONE")
}
if (!exists("final.forecast")) {
  cat(" forecasting...")
  final.forecast <- forecast(final.model, h=168*8, lambda=chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- final.model
plotting.forecast <- final.forecast
cat("AIC =",plotting.model$aic, "\n")
cat("AICc =",plotting.model$aicc, "\n")
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  ,
  residuals.acf
  ,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  ,
  residuals.pacf
  ,
  nrow = 2
))
print(plot_forecast(plotting.forecast) + autolayer(final.testing, series="Original") + ylab("Mean hourly movement (nm)"))
plots <- show_overlap_and_diff(
  final.training, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

>>>>

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("final.model")) {
  cat(" fitting...")
  final.model <- Arima(final.training, chosen.model[1:3], chosen.model[4:6], lambda=chosen.lambda)
  cat("DONE")
}
if (!exists("final.forecast")) {
  cat(" forecasting...")
  final.forecast <- forecast(final.model, h=168*8, lambda=chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- final.model
plotting.forecast <- final.forecast
print(plotting.model)
print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.acf,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.pacf,
  nrow = 2
))
print(plot_forecast(plotting.forecast) + autolayer(final.testing, series="Original") + ylab("Mean hourly movement (nm)"))
plots <- show_overlap_and_diff(
  final.training, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))
